### 2024-08-16 paper.tex
more

\section{Finding the Springer fiber at a Slodowy slice}
\par Fix any \(X \in \mathcal{N}\).
In this section we find the irreducible components of
\[\pi^{-1}(X) \cong V := \{(U, a, b) : \forall i. \; A_{X, a, b} U_{i + 1} \subseteq U_i\}.\]

\begin{lemma}
    \(V = V_0 \cup \bigcup_{w, r} V_{w,r}\), where 
    \[V_0 = \{(U, 0, b)\} \subseteq V,\]
    and
    \[V_{w,r} = \{(U, a, b) : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{X, a, b} (P, I_n) = A_{X, e_{wr}, b'} \} \subseteq V.\]
\end{lemma}
\begin{proof}
    TODO
\end{proof}
Now, we will find the irreducible components of \(V_0\) and the \(V_{w,r}\).
These will all happen to be equidimensional, so we will see that their closures in \(V\) are the irreducible components of \(V\).
\par We begin with \(V_0\), which will be easy.

>>>>

\section{Finding the Springer fiber at a Slodowy slice}
\par Fix any \(X \in \mathcal{N}\).
Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be a Jordan basis for \(X\).
For convenience we define \(e_{i0} := 0\); now we may express the fact that \((e_{ij})\) is a Jordan basis by writing \(\forall i. Xe_{ij} = e_{i,j - 1}\).
\par In this section we find the irreducible components of
\[\pi^{-1}(X) \cong V := \{(U, a, b) : \forall i. \; A_{X, a, b} U_{i + 1} \subseteq U_i\}.\]
\par For \(1 \leq w \leq k\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\)), define 
\[V_{w,r} := \{(U, a, b) \in V : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{X, a, b} (P, I_n) = A_{X, e_{wr}, b'} \}.\]

\begin{lemma}
    \(V = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} V_{w,r}\).
    Further, \(V_{w_1r_1} = V_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \(\lambda_{w_1} = \lambda_{w_2} \land r_1 = r_2\).
    When \(V_{w_1r_1} \neq V_{w_2r_2}\), we have \(V_{w_1r_1} \cap V_{w_2r_2} = \emptyset\).
\end{lemma}
\begin{proof}
    TODO
\end{proof}
Now, fix any \(w\) and \(r\).
We will find the irreducible components of \(V_{w,r}\).
These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(V\) will be the irreducible components of \(V\).
\par Let 
\[G := \{A \in \GL_m : A^{-1} X A = X\},\]
and 
\[G_{wr} := \{A \in \GL_m : \forall b. \exists b'. (A^{-1}, I_n) A_{X, e_{wr}, b} (A, I_n) = A_{X, e_{wr}, b'}\}.\]
If you write out the condition \(A_{X, e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\), it is plain to see that 
\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
\par Now, define 
\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\), defined by
\[((U, e_{wr}, b), A) \mapsto (AU, e_{wr}A, Ab)\]
